The Rapid Cycleway Prioritisation Tool

### 2020-06-15 rapid-slides.Rmd
Update slides

# How does the tool identify ‘top ranked new cycleways’?

@@

@@

See the results at:

[www.cyipt.bike/rapid/west-yorkshire](https://www.cyipt.bike/rapid/west-yorkshire)

@@

>>>>

### How to identify ‘top ranked new cycleways’?

@@

Tablular results for Leeds

```{r, echo=FALSE, out.height="100%"}
res_leeds = sf::read_sf("https://www.cyipt.bike/rapid/west-yorkshire/top_routes.geojson")
res_table = res_leeds %>%
  sf::st_drop_geometry() %>% 
  arrange(desc(mean_cycling_potential))
# %>% 
#   select(
#     Name = name,
#     Reference = ref,
#     `Length (m)` = group_length,
#     `Cycling potential` = mean_cycling_potential,
#     `Length * potential (km)` = km_cycled,
#     # `SRN` = srn,
#     `Speed limit` = speed_limit,
#     `Mean estimated width (m)` = mean_width,
#     `Majority spare lane(s)?` = majority_spare_lane
#     ) 
DT::datatable(res_table, height = 600)
```

@@

@@

See the results at [www.cyipt.bike/rapid/west-yorkshire](https://www.cyipt.bike/rapid/west-yorkshire)
